Research Report

### 2023-03-01 tex/paper-acts/main.tex
update paper, js

\n{sco}{\rom{score}}
\n{peff}{\rom{particle efficiency}}
\n{pdup}{\rom{particle duplicate rate}}
\n{pfak}{\rom{particle fake rate}}
\n{teff}{\rom{track efficiency}}
\n{tdup}{\rom{track duplicate rate}}
\n{tfak}{\rom{track fak rate}}
\n{runtime}

@@

Some terminology is described here. A \ita{sequence} is an ordered list of algorithms beginning at event generation, through CKF reconstruction, and ending at the CKF efficiency analyzer. A \ita{trial} is one sequence with one set of parameters. A \ita{score} is a number calculated given the efficiencies from one trial.

@@

\figtab{l l}{Truth Seed Range $\pt$ [MeV] & 500\\
r [mm] & 200\\
$\Delta$ r & Optimized}

@@

\item Initialize the optimizer and set the first trial paremters to \fref{192837a}.

@@

\figpic{4cm}{/home/user1/time/2023-02-23/2023-02-23-11-14/single/dup.png}{Initial track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
\figpic{4cm}{/home/user1/time/2023-02-23/2023-02-23-11-14/single/eff.png}{Initial track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
\figpic{4cm}{/home/user1/time/2023-02-23/2023-02-23-11-14/single/fak.png}{Initial track fake fraction as function of $\eta$, $\phi$, and $\pt$.}

@@

\e{\sco = \preff - \tfak - \tdup / 5 - \runtime / 5}

@@

Max Seeds Per Middle Space Point [n] & 0 $\pm$0\\

@@

@@

\figpic{6cm}{/home/user1/time/2023-02-21/2023-02-21-23-06-52/score.png}{Plot of score per trial.}

@@

The parameters from the trial with the highest score were used to generate 100 events, with 100 pileup particles each. The resulting efficiency plots are below.,
\figpic{4cm}{/home/user1/time/2023-02-22/2023-02-22-13-30/compare-4/dup.png}{Track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
\figpic{4cm}{/home/user1/time/2023-02-22/2023-02-22-13-30/compare-4/eff.png}{Track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
\figpic{4cm}{/home/user1/time/2023-02-22/2023-02-22-13-30/compare-4/fak.png}{Track fake fraction as function of $\eta$, $\phi$, and $\pt$.}

@@

\figpic{6\cm}{/home/user1/time/2023-02-22/2023-02-22-18-01-01/score.png}{Plot of score per trial}
\figpic{9\cm}{/home/user1/time/2023-02-22/2023-02-22-18-01-01/parameter_per_trial/grid.png}{Parameters per trial.}
\figpic{9\cm}{/home/user1/time/2023-02-22/2023-02-22-18-01-01/efficiency_per_trial/grid.png}{Efficiency per trial.}
The parameters from the trial with the highest score were used to generate 100 events, with 100 pileup particles each. The resulting efficiency plots are below.,
\figpic{4cm}{/home/user1/time/2023-02-23/2023-02-23-04-19/compare-4/dup.png}{Track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
\figpic{4cm}{/home/user1/time/2023-02-23/2023-02-23-04-19/compare-4/eff.png}{Track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
\figpic{4cm}{/home/user1/time/2023-02-23/2023-02-23-04-19/compare-4/fak.png}{Track fake fraction as function of $\eta$, $\phi$, and $\pt$.}

@@

\figpic{6cm}{/home/user1/time/2023-02-22/2023-02-22-21-04-06/score.png}{Plot of score per trial}

@@

The parameters from the trial with the highest score were used to generate 100 events, with 100 pileup particles each. The resulting efficiency plots are below.,
\figpic{4cm}{/home/user1/time/2023-02-23/2023-02-23-02-45/compare-2/dup.png}{Track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
\figpic{4cm}{/home/user1/time/2023-02-23/2023-02-23-02-45/compare-2/eff.png}{Track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
\figpic{4cm}{/home/user1/time/2023-02-23/2023-02-23-02-45/compare-2/fak.png}{Track fake fraction as function of $\eta$, $\phi$, and $\pt$.}

@@

\e{\sco=\preff - \tfak - \tdup/5}
\figpic{6cm}{/home/user1/time/2023-02-23/2023-02-23-05-10-03/score.png}{Plot of score per trial}

@@

The parameters from the trial with the highest score were used to generate 100 events, with 100 pileup particles each. The resulting efficiency plots are below.,
\figpic{4cm}{/home/user1/time/2023-02-23/2023-02-23-10-07/compare-1/dup.png}{Track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
\figpic{4cm}{/home/user1/time/2023-02-23/2023-02-23-10-07/compare-1/eff.png}{Track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
\figpic{4cm}{/home/user1/time/2023-02-23/2023-02-23-10-07/compare-1/fak.png}{Track fake fraction as function of $\eta$, $\phi$, and $\pt$.}

@@

\figpic{6cm}{/home/user1/time/2023-02-23/2023-02-23-12-34-56/score.png}{Plot of score per trial}

@@

The parameters from the trial with the highest score were used to generate 100 events, with 100 pileup particles each. The resulting efficiency plots are below.,
\figpic{4cm}{/home/user1/time/2023-02-24/2023-02-24-07-07/compare-2/dup.png}{Track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
\figpic{4cm}{/home/user1/time/2023-02-24/2023-02-24-07-07/compare-2/eff.png}{Track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
\figpic{4cm}{/home/user1/time/2023-02-24/2023-02-24-07-07/compare-2/fak.png}{Track fake fraction as function of $\eta$, $\phi$, and $\pt$.}

@@

% \figpic{7cm}{2023-01-13-00-07-47/Particle efficiency.png}{Particle efficiency when using $\eta$ from -1 to 1.}
% \figpic{7cm}{2023-01-13-00-07-47/Track duplicate rate.png}{Track duplicate rate when using $\eta$ from -1 to 1.}
% \figpic{7cm}{2023-01-13-00-07-47/Track fake rate.png}{Track fake rate when using $\eta$ from -1 to 1.}
% \subsection{Full $\eta$ Range}
% 100 trials of \ttbar event in the ODD were simulated, and reconstructed using the CKF. This table shows the optimizer's parameters after 100 trials.
% These plots show the change in reconstruction performance per trial.
% \figpic{7cm}{score.png}{Plot of \eqref{score}, the score of each trial during optimization. This shows the optimizer is successfully increasing the score of each trial.}
% \figpic{7cm}{Particle efficiency.png}{Plot of \eqref{eff}, the particle efficiency as a function of number of trials.}
% \figpic{7cm}{Track fake rate.png}{Plot of \eqref{trackfakerate}, the track fake rate as a function of number of trials.}
% \figpic{7cm}{Track duplicate rate.png}{Plot of \eqref{trackduplicaterate}, the track duplicate rate as a function of number of trials.}
% These plots show the change in reconstruction parameters per trial.
% \figpic{7cm}{cotThetaMax.png}{cotThetaMax}
% \figpic{7cm}{deltaRMax.png}{deltaRMax}
% \figpic{7cm}{deltaRMin.png}{deltaRMin}
% \figpic{7cm}{impactMax.png}{impactMax}
% \figpic{7cm}{maxPtScattering.png}{maxPtScattering}
% \figpic{7cm}{maxSeedsPerSpM.png}{maxSeedsPerSpM}
% \figpic{7cm}{radLengthPerSeed.png}{radLengthPerSeed}
% \figpic{7cm}{sigmaScattering.png}{sigmaScattering}
% For simulated \ttbar events, the CKF tracking reconstruction efficiency goes from 80\% near 10 GeV $\pt$~to 65\% near 80 GeV $\pt$. The tracking efficiency as a function of $|\eta|$ is 80\% near $|\eta|$=0, and falls to 50\% near $|\eta|$=3. The tracking efficiency appears uncorrelated as a function of coordinate $\phi$.
% \section{Discussion}
% The performance of the CKF reconstruction without any optimization of initial parameters will be used to benchmark further studies that attempt to optimize the seeding and tracking parameters.
% \section{Conclusion}
% \ttbar events were simulated using Pythia, and evaulated using the ACTS Combinatorial Kalman Filter. Future studies will run optimization algorithms on the ACTS tracking parameters to improve tracking performance.
% \section{Appendix}
% \subsection{List of Symbols}
% \begin{center}
% \begin{tabular}{l l}
% Symbol & Description\\
% B & Magnetic Field [T]\\
% \pt & Transverse momentum [eV]
% \end{tabular}
% \end{center}
% Using the parameters in and the optimization procedure in the optimized parameters are found. The efficiency plots as function of eta, phi, and pt use as parameters the CKF minimum pt and minimum number of measurements.

>>>>

\n{sco}{\rom{Score}}
\n{peff}{\rom{Particle Efficiency [frac]}}
\n{pdup}{\rom{Particle Duplicates [frac]}}
\n{pfak}{\rom{Particle Fakes [frac]}}
\n{teff}{\rom{Track Efficiency [frac]}}
\n{tdup}{\rom{Track Duplicates [frac]}}
\n{tfak}{\rom{Track Fakes [frac]}}
\n{runtime}{\rom{Runtime [s]}}

@@

@@

% \figtab{l l}{Truth Seed Range $\pt$ [MeV] & 500\\
% r [mm] & 200\\
% $\Delta$ r & Optimized}{}

@@

\item Initialize the optimizer and set the first trial paremters to \tref{192837a}.

@@

\figpic{3.5cm}{/home/user1/time/2023-02-23/2023-02-23-11-14/single/dup.png}{Initial track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
\figpic{3.5cm}{/home/user1/time/2023-02-23/2023-02-23-11-14/single/eff.png}{Initial track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
\figpic{3.5cm}{/home/user1/time/2023-02-23/2023-02-23-11-14/single/fak.png}{Initial track fake fraction as function of $\eta$, $\phi$, and $\pt$.}

@@

\e{\sco = \peff - \tfak - \tdup / 5 - \runtime / 5}

@@

Max Seeds Per Middle Space Point [n] & 0 $\pm$ 0\\

@@

This optimization was run 7 separate times, 100 trials each, to test how large the uncertainties are on the best trial parameters. No efficiency plots are shown.

@@

\figpic{6cm}{/home/user1/time/2023-02-21/2023-02-21-23-06-52/score.png}{Optimizer score per trial..}

@@

The parameters from the trial with the highest score were used to generate 100 events, with 100 pileup particles each. The resulting efficiency plots are below.
\figpic{3.5cm}{/home/user1/time/2023-02-22/2023-02-22-13-30/compare-4/dup.png}{Track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
\figpic{3.5cm}{/home/user1/time/2023-02-22/2023-02-22-13-30/compare-4/eff.png}{Track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
\figpic{3.5cm}{/home/user1/time/2023-02-22/2023-02-22-13-30/compare-4/fak.png}{Track fake fraction as function of $\eta$, $\phi$, and $\pt$.}

@@

\figpic{6cm}{/home/user1/time/2023-02-22/2023-02-22-18-01-01/score.png}{Optimizer score per trial.}
\figpic{9cm}{/home/user1/time/2023-02-22/2023-02-22-18-01-01/parameter_per_trial/grid.png}{Parameters per trial.}
\figpic{9cm}{/home/user1/time/2023-02-22/2023-02-22-18-01-01/efficiency_per_trial/grid.png}{Efficiency per trial.}
The parameters from the trial with the highest score were used to generate 100 events, with 100 pileup particles each. The resulting efficiency plots are below.
\figpic{3.5cm}{/home/user1/time/2023-02-23/2023-02-23-04-19/compare-4/dup.png}{Track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
\figpic{3.5cm}{/home/user1/time/2023-02-23/2023-02-23-04-19/compare-4/eff.png}{Track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
\figpic{3.5cm}{/home/user1/time/2023-02-23/2023-02-23-04-19/compare-4/fak.png}{Track fake fraction as function of $\eta$, $\phi$, and $\pt$.}

@@

\figpic{6cm}{/home/user1/time/2023-02-22/2023-02-22-21-04-06/score.png}{Optimizer score per trial.}

@@

The parameters from the trial with the highest score were used to generate 100 events, with 100 pileup particles each. The resulting efficiency plots are below.
\figpic{3.5cm}{/home/user1/time/2023-02-23/2023-02-23-02-45/compare-2/dup.png}{Track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
\figpic{3.5cm}{/home/user1/time/2023-02-23/2023-02-23-02-45/compare-2/eff.png}{Track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
\figpic{3.5cm}{/home/user1/time/2023-02-23/2023-02-23-02-45/compare-2/fak.png}{Track fake fraction as function of $\eta$, $\phi$, and $\pt$.}

@@

\e{\sco=\peff - \tfak - \tdup/5}
Max \textrm{cot}($\theta$) [\textrm{cot}($\theta$)] & 9.894147867588261\\
Max $\Delta R$ [mm] & 78.45827959526429\\
Min $\Delta R$ [mm] & 22.770804208643327\\
Max $r_\textrm{impact}$ [mm] & 17.264025370752\\
Max scattering $p_{\textrm{T}}$ [GeV] & 22.138871404772974\\
Max Seeds Per Middle Space Point [n] & 7\\
Radiation Length Per Seed & 0.001526817277071645\\
Scattering $\sigma$ [$\sigma$] & 33.877560589074356 
\figpic{6cm}{/home/user1/time/2023-02-23/2023-02-23-05-10-03/score.png}{Optimizer score per trial.}

@@

The parameters from the trial with the highest score were used to generate 100 events, with 100 pileup particles each. The resulting efficiency plots are below.
\figpic{3.5cm}{/home/user1/time/2023-02-23/2023-02-23-10-07/compare-1/dup.png}{Track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
\figpic{3.5cm}{/home/user1/time/2023-02-23/2023-02-23-10-07/compare-1/eff.png}{Track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
\figpic{3.5cm}{/home/user1/time/2023-02-23/2023-02-23-10-07/compare-1/fak.png}{Track fake fraction as function of $\eta$, $\phi$, and $\pt$.}

@@

Max \textrm{cot}($\theta$) [\textrm{cot}($\theta$)] & 9.866139016895074\\
Max $\Delta R$ [mm] & 183.62476842099014\\
Min $\Delta R$ [mm] & 27.017826961402342\\
Max $r_\textrm{impact}$ [mm] & 16.705994491748385\\
Max scattering $p_{\textrm{T}}$ [GeV] & 46.36841479558609\\
Radiation Length Per Seed & 0.09965229969028085\\
Scattering $\sigma$ [$\sigma$] & 1.5604089909909047 
\figpic{6cm}{/home/user1/time/2023-02-23/2023-02-23-12-34-56/score.png}{Optimizer score per trial.}

@@

The parameters from the trial with the highest score were used to generate 100 events, with 100 pileup particles each. The resulting efficiency plots are below.
\figpic{3.5cm}{/home/user1/time/2023-02-24/2023-02-24-07-07/compare-2/dup.png}{Track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
\figpic{3.5cm}{/home/user1/time/2023-02-24/2023-02-24-07-07/compare-2/eff.png}{Track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
\figpic{3.5cm}{/home/user1/time/2023-02-24/2023-02-24-07-07/compare-2/fak.png}{Track fake fraction as function of $\eta$, $\phi$, and $\pt$.}

@@

% \figpic{7cm}{2023-01-13-00-07-47/Particle efficiency.png}{Particle efficiency when using $\eta$ from -1 to 1.}
% \figpic{7cm}{2023-01-13-00-07-47/Track duplicate rate.png}{Track duplicate rate when using $\eta$ from -1 to 1.}
% \figpic{7cm}{2023-01-13-00-07-47/Track fake rate.png}{Track fake rate when using $\eta$ from -1 to 1.}
% \subsection{Full $\eta$ Range}
% 100 trials of \ttbar event in the ODD were simulated, and reconstructed using the CKF. This table shows the optimizer's parameters after 100 trials.
% These plots show the change in reconstruction performance per trial.
% \figpic{7cm}{score.png}{Plot of \eqref{score}, the score of each trial during optimization. This shows the optimizer is successfully increasing the score of each trial.}
% \figpic{7cm}{Particle efficiency.png}{Plot of \eqref{eff}, the particle efficiency as a function of number of trials.}
% \figpic{7cm}{Track fake rate.png}{Plot of \eqref{trackfakerate}, the track fake rate as a function of number of trials.}
% \figpic{7cm}{Track duplicate rate.png}{Plot of \eqref{trackduplicaterate}, the track duplicate rate as a function of number of trials.}
% These plots show the change in reconstruction parameters per trial.
% \figpic{7cm}{cotThetaMax.png}{cotThetaMax}
% \figpic{7cm}{deltaRMax.png}{deltaRMax}
% \figpic{7cm}{deltaRMin.png}{deltaRMin}
% \figpic{7cm}{impactMax.png}{impactMax}
% \figpic{7cm}{maxPtScattering.png}{maxPtScattering}
% \figpic{7cm}{maxSeedsPerSpM.png}{maxSeedsPerSpM}
% \figpic{7cm}{radLengthPerSeed.png}{radLengthPerSeed}
% \figpic{7cm}{sigmaScattering.png}{sigmaScattering}
% For simulated \ttbar events, the CKF tracking reconstruction efficiency goes from 80\% near 10 GeV $\pt$~to 65\% near 80 GeV $\pt$. The tracking efficiency as a function of $|\eta|$ is 80\% near $|\eta|$=0, and falls to 50\% near $|\eta|$=3. The tracking efficiency appears uncorrelated as a function of coordinate $\phi$.
% \section{Discussion}
% The performance of the CKF reconstruction without any optimization of initial parameters will be used to benchmark further studies that attempt to optimize the seeding and tracking parameters.
% \section{Conclusion}
% \ttbar events were simulated using Pythia, and evaulated using the ACTS Combinatorial Kalman Filter. Future studies will run optimization algorithms on the ACTS tracking parameters to improve tracking performance.
% \section{Appendix}
% \subsection{List of Symbols}
% \begin{center}
% \begin{tabular}{l l}
% Symbol & Description\\
% B & Magnetic Field [T]\\
% \pt & Transverse momentum [eV]
% \end{tabular}
% \end{center}
% Using the parameters in and the optimization procedure in the optimized parameters are found. The efficiency plots as function of eta, phi, and pt use as parameters the CKF minimum pt and minimum number of measurements.
% Some terminology is described here. A \ita{sequence} is the ordered list of algorithms beginning at event generation, through particle propagation, CKF reconstruction, and ending at the CKF efficiency analyzer. A \ita{trial} is one sequence and one set of parameters. A \ita{score} is the number calculated given the efficiencies from one trial.
